% Template for IEEEtransactions
% Adapted by Sik in March 2016 to meet his requirements
%
\documentclass[10pt,conference,a4paper]{latex/IEEEtran}
%% Latex documents that need direct input
%
\input{./latex/filesystem/ieee_packages.tex}  % contains the latex packages for IEEEtrans
\input{./latex/filesystem/package.tex}        % contains the latex packages
% \input{./latex/filesystem/package_edition.tex}% contains the latex packages
% \usepackage[numbers]{natbib}
\input{latex/filesystem/fileSetup.tex}        % contains package and variables init.
\input{content/acronym_definition.tex}      % contains the acronims

%% Select inputing only one part of the document
%\includeonly{content/intro/intro}   % the file wihtout .tex
%\includeonly{content/other/other_content}

% \addbibresource{./content/lit_review.bib}
% \addbibresource{./content/biblatex-examples.bib}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\input{content/frontmatter.tex}             % contains the Title and Autor info

\maketitle

% Please keep the abstract below 300 words
\begin{abstract}
This article reviews the current state of automatic classification methodologies to identify \gls{dme} versus normal subjects based on \gls{sdoct} data.
Addressing this classification problem has valuable interest since early detection and treatment of \gls{dme} play a major role to prevent eye adverse effects such as blindness.

The main contribution of this article is to cover the lack of a public dataset and benchmark suited for classifying \gls{dme} and normal \gls{sdoct} volumes, providing our own implementation of the most relevant methodologies in the literature.
Subsequently, 6 different methods were implemented and evaluated using this common benchmark and dataset to produce reliable comparison.

\end{abstract}

\begin{IEEEkeywords}
  \glsresetall % reset the acronyms from the abstract
  \gls{dme},
  \gls{sdoct},
  \gls{ml},
  benchmark,
\end{IEEEkeywords}

% \linenumbers

%% Incldue the content without .tex extension
\glsresetall % reset the acronyms from the abstract
\include*{content/intro/intro}          % the file wihtout .tex
\include*{content/survey/background}
\include*{content/method/dataset}
\input{./content/results/table_summary}
\include*{content/method/method}
\include*{content/results/results}
% \section{Discussion}\label{sec:discussion}
\section{Conclusion and Further work}\label{sec:conclusion}
The work here presented states the relevance of developing methodologies to automatically differentiate \gls{dme} \emph{vs.} normal \gls{sdoct} scans.
This article offers an overview of the state-of-the-art of \gls{dme} detection and provides a public benchmarking to facilitate further studies.
In this regard, there are two crucial aspects to improve the work here presented:
(i) enlarge the dataset.
%(ii) reach out for the other authors of those methods in Sect.\,\ref{sec:review} that could not be included in Sect.\,\ref{sec:exp} because our implementation could not be tested against the original data or we did not achieve the original results.
(ii) reach out to other authors in order to enlarge this benchmark with additional methods and improve the existing approaches.

% \nolinenumbers

%\section*{References}
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.

% % Imports the bibliography file "sample.bib"
% \bibliography{sample}
\bibliographystyle{IEEEtran}
\IEEEtriggeratref{17}
\bibliography{content/bib/literature_review,content/bib/medical/medical,content/bib/retinopathy/retinopathy}

\end{document}
