% include the figures path relative to the master file
\graphicspath{ {./content/intro/figures/} }

\section{Introduction}
\label{sec:intro}  % \label{} allows reference to this section

\gls{dr} and \gls{dme} are leading causes of irreversible vision loss and the most common eye diseases in individuals with diabetes.
Taking into account that the number of individuals affected by diabetes dieases are expected to grow exponentially in the next decade~\cite{wild2004global},
developing methodologies for early detection and treatment of \gls{dr} and \gls{dme} has become a priority to prevent adverse effects such as blindness.
%Number of people affected by diabetes are expected to grow exponentionally affecting over \SI{300}{M} pople worldwide by 2025~\cite{Wild2004}.
%Just in United States alone, health care and associated costs related to eye diseases are estimated at almost \SI{500}[\$]{M}~\cite{Sharma2005}.
%Moreover, the prevalent cases of \gls{dr} are expected to grow exponentially affecting over \SI{300}{M} people worldwide by 2025~\cite{Wild2004}.
%Given this scenario, early detection and treatment of \gls{dr} and \gls{dme} play a major role to prevent adverse effects such as blindness.

%\gls{dme} is characterized as an increase in retinal thickness within 1 disk diameter of the fovea center with or without hard exudates and sometimes associated with cysts~\cite{ETDRSG1985}.
The main focus of this work is to describe the actual state of \gls{dme} detection in \gls{oct} images.
\gls{dme} presents an increase in retinal thickness within 1 disk diameter of the fovea center with or without hard exudates and sometimes associated with cysts~\cite{ETDRSG1985}.
\gls{sdoct} is an emerging eye imaging modality providing corss-sectional retinal morphology information~\cite{Wang2015}, which cannot be estimated from more established eye imaging modalities such as fundus imaging.

The initial efforts of the ophtalmic community in developing technologies for \gls{sdoct}, have been placed in segmenting the retinal layers, which is a necessary step for retinal thickness measurements~\cite{Chiu2010,Kafieh2013}.
However, latter efforts address the specific problem of \gls{dme} automatic detection in \gls{oct} volumes, which revealed the need for addressing: (i) enhancing \gls{oct} volumes, (ii) finding pathology signs, or (iii) appropriated classification strategies.

Advances in any of those regards is of great interest since (i) manual evaluation of \gls{sdoct} volumetric scans is expensive and time consuming~\cite{Venhuizen2015}.
%(ii) \gls{sdoct} acquisition has some deficiencies due to eye movement during the scan~\cite{Liu2011}, the reflectivity nature of the retina~\cite{schuman2004optical}, the fact that \gls{oct} suffers from high levels of noise and the overall image quality is inconsistent~\cite{barnum2008local}.
(ii) \gls{sdoct} acquisition has some shortcomings due to eye movement in the scan~\cite{Liu2011}, reflectivity nature of the retina~\cite{schuman2004optical}, high level of noise and inconsistent quality of the images. 
%(iii) Coexistence of multiple pathologies~\cite{Liu2011}, easy to miss pathology signs~\cite{Venhuizen2015}, or large variability within the pathology treats which difficult to obtain proper radiomix to facilitate the task of classification.
(iii) Due to coexistence of multiple pathologies~\cite{Liu2011} and large variability within the pathology treates it is difficult to obtain the proper sign for each pathology and moreover it is easy to miss them~\cite{Venhuizen2015}.


The rest of this article is structured as follows: Section~\ref{sec:review} offers a general idea of the literature state-of-the-art in \gls{sdoct} volume classification. Section~\ref{sec:data} reviews some publicly available datasets and states the need for another one that suits the classification task here described.
Section~\ref{sec:exp} proposes an experimental benchmark to compare different methodologies presented in Sect.\,\ref{sec:review}.
Section~\ref{sec:results} reports and discusses the obtained results, while Sect.\,\ref{sec:conclusion} wraps up our thoughts regarding this work and its possible direction.

% Some stuff that emac's colegues use
%%% Local Variables:
%%% mode: late
%%% TeX-master: "../../main.tex"
%%% End: \section{introduction}

